### 2016-03-28 WRITEUP/Obs.tex
take into account DR's comments on cosmetics

\section{Observations}
\subsection{PdBI} \label{sec:PdBIdata}
Observations of the CO($J$ = 2 $\rightarrow$ 1) rotational line ($\nu_{\rm
rest}$ = 230.5379938 GHz) toward the background galaxy RXJ1131-1231 at $z$ = 
0.655BLAH
 were carried out using IRAM Plateau de Bure Interferometer (PdBI) at the
redshifted frequency of $\nu_{\rm obs}$ = 
 BLAH GHz (BLAH mm) (Program ID: S14BX001; PI: D. Riechers). 
 Two observing runs were carried out on 2014 Dec 06 and 2015 Feb 05 under good
%2 mm
weather conditions in the C and D array configurations, respectively. The 2 mm
receivers were used to cover the redshifted CO($J$ = 2 $\rightarrow$ 1) line
and the 
underlying continuum emission (rest frame BLAH = (2.152 * (1+z)) mm), employing
a correlator setup providing an effective bandwidth of 3.16 GHz and spectral 
resolution of 10.0 MHz ($\sim$21.5281 km s$^{-1}$).
This resulted in 3.74 hours of cumulative six antenna-equivalent on-source time

@@

The GILDAS package was used to reduce and analyze the visibility data which are
then imaged and deconvolved using
the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean
beam size of 4$\farcs$44 $\times$ 1\farcs95. The final rms noise is $\sigma$ =
0.177 
Jy km s$^{-1}$ beam$^{-1}$ over a channel width of 320 MHz (corresponding to
690 km s$^{-1}$), and $\sigma$ = 1.451 Jy km s$^{-1}$ beam$^{-1}$ over 10 MHz 
(21.5 km s$^{-1}$) . 
The continuum image is created by % 2.152 mm; 
averaging over all the line-free channels ($\nu_{\rm cont}\sim$139 GHz). This
yields an rms noise of 0.082 mJy beam$^{-1}$. % see README.md in 04Sep15

\subsection{CARMA} \label{sec:carmadata}
% LO = 215.6694 Ghz
% 3C273 FG
% 3C279 Bandpass
% mars flux
% after flagging: Total observing time is  1.48 hours, checked with uvindex
%
Observations of the CO($J$ = 3 $\rightarrow$ 2) rotational line ($\nu_{\rm
rest}$ = 345.7959899 GHz) toward the background galaxy RXJ1131-1231 at $z$ = 
0.655BLAH 
 were carried out using the Combined Array for Research in Millimeter-wave
Astronomy (CARMA) at the redshifted frequency of $\nu_{\rm obs}$ = BLAH GHz
(BLAH 
mm) (Program ID: cf0098; PI: D. Riechers).
observations were carried out on 2014 February 17 under good 3 mm weather
conditions in the D array configurations. The 3 mm receivers were used to cover
the 
redshifted CO($J$ = 3 $\rightarrow$ 2) line, employing a correlator setup
providing a bandwidth of 3.75 GHz in each sideband and spectral resolution of
12.5 MHz ($
\sim$17BLAH km s$^{-1}$). The line was placed in the
lower sidebands with the local oscillator tuned to $\nu_{\rm LO}\sim$ 216 GHz;
this resulted in 1.5 hours of 15 antenna-equivalent on-source time after
discarding 
unusable visibility data.

The nearby radio quasar 3C273 was observed every 15 minutes for
pointing, amplitude, and phase calibration, and Mars was observed as the
primary
absolute flux calibrator. 3C279 was observed as bandpass calibrators, yielding
$\sim
$15\%BLAH calibration accuracy.
The MIRIAD package was used to calibrate and analyze the visibility data which
are imaged and deconvolved using
the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean
beam size of 3\farcs1 $\times$ 1\farcs9 for the lower sideband image cube. The
final 
rms noise is $\sigma$ = BLAH Jy km s$^{-1}$ beam$^{-1}$ over a channel width of
BKAH MHz (corresponding to BLAH km s$^{-1}$). 
The continuum image is created by
averaging over all the line-free channels ($\nu_{\rm cont}\sim$216 GHz). This
yields a synthesized clean beam size of Blah\farcs5 $\times$ blah\farcs0 and an
rms 
noise of 0.24Blah mJy beam$^{-1}$.

>>>>

\section{Observations}
\subsection{PdBI} \label{sec:PdBIdata}
Observations of the CO($J$ = 2 $\rightarrow$ 1) rotational line ($\nu_{\rm
rest}$ = 230.5379938 GHz) toward the background galaxy RXJ1131-1231 at $z$ = 
0.655BLAH
 were carried out using IRAM Plateau de Bure Interferometer (PdBI) at the
redshifted frequency of $\nu_{\rm obs}$ = 
 BLAH GHz (BLAH mm) (Program ID: S14BX001; PI: D. Riechers). 
 Two observing runs were carried out on 2014 Dec 06 and 2015 Feb 05 under good
%2 mm
weather conditions in the C and D array configurations, respectively. The 2 mm
receivers were used to cover the redshifted CO($J$ = 2 $\rightarrow$ 1) line
and the 
underlying continuum emission (rest frame BLAH = (2.152 * (1+z)) mm), employing
a correlator setup providing an effective bandwidth of 3.6 GHz and spectral 
resolution of 10.0 MHz ($\sim$21.5281 km s$^{-1}$).
This resulted in 3.74 hours of cumulative six antenna-equivalent on-source time

@@

The GILDAS package was used to reduce and analyze the visibility data which are
then imaged and deconvolved using
the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean
beam size of 4$\farcs$44 $\times$ 1\farcs95 (PA: 13\degr). The final rms noise is $\sigma$ =
0.177 
Jy km s$^{-1}$ beam$^{-1}$ over a channel width of 320 MHz (corresponding to
690 km s$^{-1}$), and $\sigma$ = 1.451 Jy km s$^{-1}$ beam$^{-1}$ over 10 MHz 
(21.5 km s$^{-1}$) . 
The continuum image is created by % 2.152 mm; 
averaging over all the line-free channels ($\nu_{\rm cont}\sim$139 GHz). This
yields an rms noise of 0.082 mJy beam$^{-1}$. % see README.md in 04Sep15

\subsection{CARMA} \label{sec:carmadata}
% LO = 215.6694 Ghz
% 1127-189 Gain for set 2
% 3C273 gain for set 3
% 3C279 Bandpass for both
% mars flux for both
% after flagging: Total observing time is  1.48 hours, checked with uvindex for
set 3
% after flagging: Total obs. time is 2.94 hours, checked with uvindex for the
combined set
% 12.500 GHz <=> 17.935 km/s
%
Observations of the CO($J$ = 3 $\rightarrow$ 2) rotational line ($\nu_{\rm
rest}$ = 345.7959899 GHz) toward the background galaxy RXJ1131-1231 at $z$ = 
0.655BLAH 
 were carried out using the Combined Array for Research in Millimeter-wave
Astronomy (CARMA) at the redshifted frequency of $\nu_{\rm obs}$ = BLAH GHz
(BLAH mm) (Program ID: cf0098; PI: D. Riechers).
observations were carried out on 2014 February 17 under good 3 mm weather
conditions and on 2014 February 02 under terrible 3mm weather in the D array
configurations.

The 3 mm receivers were used to cover
the 
redshifted CO($J$ = 3 $\rightarrow$ 2) line, employing a correlator setup
providing a bandwidth of 3.75 GHz in each sideband and spectral resolution of
12.5 MHz ($
\sim$17.9 km s$^{-1}$). The line was placed in the
lower sidebands with the local oscillator tuned to $\nu_{\rm LO}\sim$ 216 GHz;
this resulted in 2.94 hours of 15 antenna-equivalent on-source time after
discarding 
unusable visibility data.

The radio quasars 3C273 and J1127-189 was observed every 15 minutes for
pointing, amplitude, and phase calibration. Mars was observed as the
primary
absolute flux calibrator and 3C279 was observed as bandpass calibrators for
both tracks. 
The phase calibrator J1127-189 from the first track is faint and observed under
poor weather and the phase calibrator 3C273 is far from source for the second
track. Hence, the phase calibration was 
subpar, with rms scatter $\sim$ 60\degr, 
yielding
$\sim
$20\% calibration accuracy.
The MIRIAD package was used to calibrate and analyze the visibility data which
are imaged and deconvolved using
the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean
beam size of 3\farcs2 $\times$ 1\farcs9 (PA: 8\degr) for the lower sideband
image cube. The
final 
rms noise is $\sigma$ = 13.3 mJy km s$^{-1}$ beam$^{-1}$ over a channel width
of
25 MHz (corresponding to 35.87 km s$^{-1}$).

### 2016-03-28 WRITEUP/Results.tex
take into account DR's comments on cosmetics

\documentclass[]{emulateapj}
\usepackage{amsmath}
\begin{document}
\author{Draft}

\section{HST astrometry}
We adopt the VLA 5\,GHz map as the reference coordinate frame and shift the
coordinate frame in the optical image to this one to align the emission.

Employed local phase calibrator, with positions known to $\sim$1 mas, estimate
the absolute alignment of the 5 GHz and CO(J=2-1) coordinate frames should
be better than 0.1", leaving aside uncertainties relating to SNR and beam size.

The astrometry of the HST images was firstly calibrated against a wider-field
optical image of the cluster which had in turn been aligned onto the FK5
coordinate system to an rms precision of ~0.2".

%The align the IRAM data (2-mm continuum and CO(J=2-1)) with the VLA 5-GHz
%continuum emission, we shifted the former to the east by BLAH" in R.A., which is
%consistent with the claimed astrometric precision of the PdBI images.

To align the optical/NIR data with the VLA 5-GHz continuum emission, we
shifted the former in Dec. by +BLAH".

@@

Analysis using both set 2 and set 3 observations.

natural weighting beam size:  3.19 x 1.86 PA: 8 deg
channel width = 2x17.935 = 35.87 km/s
rms = 1.32997E-02 Jy/B/channel

 Integrated line flux = 37.509 Jy km/s over chan=[49,70] (FWZI)
%- ! Parameters and Errors:
%- ! MFIT%PAR[01]  
%- ! MFIT%PAR[02]  
%- ! MFIT%PAR[03]  
%- ! MFIT%PAR[04]  
%- velocity range [,] km/s

We have detected unresolved CO($J$ = 3 $\rightarrow$ 2) line emission toward
SMM J0939+8315 at peak flux at blah $\sigma$ signifcance of $ \sigma$ = 13.2997

mJy beam$^{-1}$.

We detect unresolved CO($J$ = 3 $\rightarrow$ 2) line emission toward the
background galaxies in RXJ1131-1231. 
We extract the spectrum and fit a single-component Gaussian as shown in Figure
\ref{fig:}
yielding peak flux density of BLAH $\pm$ BLAH mJy, the FWHM of the Gaussian fit
is BLAH $\pm$ BLAH km s$^{-1}$.

\begin{figure}[tbph]
\centering
\includegraphics[width=0.5\textwidth]{../Figures/co32_spec_bin2.eps}	  
\caption{
CO32 line spectrum
 \label{fig:}}
\end{figure}

We made a 1.4mm continuum map using line-free channels, $\sigma$ = 8.30807E-04
Jy/B

At spatial position of CO emission, No significant continuum emission was
detected from the line-free region down to a 3$\sigma$ limit of blah mJy
(burried in noise - 
2.2 $\pm$ 3.0 mJy). Hence, we place a 3$\sigma$ upper limit of BLAH.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{CO($J$ = 2 $\rightarrow$ 1) line emission}
natural weighting beam size: 4.44 x 1.95, PA 13deg
rms = ~ 1.451 mJy/ Beam/ch
velocity resolution per bin: 21.528154 km/s
source extent?

@@

We construct the velocity-integrated (0th moment) map of the CO($J$ = 2
$\rightarrow$ 1) emission using the uv-continuum subtracted data, the
velocity-integrated 
CO($J$ = 2 $\rightarrow$ 1) line flux is 20.3 $\pm$ BLAH Jy km s$^{-1}$.

% upper limit on other lines 
% in the foreground galaxy -- HNC (J=2-1)

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.35\textwidth]{../Figures/{F555WCO21_mom0_single.invertedgray}.eps}	   
\includegraphics[width=0.35\textwidth]{../Figures/F555W_REDCentBLUE.png}
\includegraphics[width=0.55\textwidth]{../Figures/SpecCO21_twinx.eps}
\caption{
0th Moment map of CO(2-1) emission on HST F555W. moment-0: no clipping
Spectrum. Velocity scale w.r.t z=0.655
 \label{fig:CO21mom0}}
\end{figure*}

\begin{figure}[tbph]
\centering
\includegraphics[width=0.5\textwidth]{../Figures/CO_highOmom_CLIP5sigma}       
\caption{
1st and 2nd order moments, clipped at 5 $\sigma$
TODO: enlarge and choose better velocity interval
 \label{fig:}}
\end{figure}

\begin{figure*}[tbph]
\centering
\includegraphics[width=\textwidth]{../Figures/co_channel_maps.eps}	 %
\caption{
Black crosses indicate the position of the lensed AGN (components ABCD) and the
foreground lensing galaxy (component G) in the HST image.
TODO: Change sym for fg gal., add one chan before and after first and last.; change colorbar scale to mJy/B, add tick in negative direction. try 3sigma steps to see if can show more structures in channel slice
 \label{fig:chanmap}}
\end{figure*}

\begin{figure*}[tbph]
\centering
\includegraphics[width=\textwidth]{../Figures/spatialSpec_offsetShifted.eps}   
\caption{ 
Spatial spectra, binned by 3 pixels in each direction (1\farcs5)
TODO: add velo scale; larger labels for pixel pos
 \label{fig:spatialSpec}}
\end{figure*}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{SED}
\begin{figure*}[tbph]
\centering
\includegraphics[width=0.8\textwidth]{../Figures/FullSED.eps}	 
\caption{VLA 5GHz continuum and PdBI 2mm continuum
TODO: change sym indicating the VLA data, (now two points at the same frequency), change sym for the 2 points on 2mm PdBI (now integrated and peak), might want to extract flux after removing a point source model.
WANT TO MAKE SED FITTING with POWER LAW including the one point from 24.0\micron, from Spitzer/MIPS .
Note THAT the WISE flux is higher than the IRAC data, probably just due to the smaller aperture used in Spitzer flux extraction, which might not be resolving the source and not including everything. 
Might want to add NVSS constraints.

 \label{fig:}}
\end{figure*}

>>>>

\documentclass[]{emulateapj}
\usepackage{amsmath}
\input{preamble}
\begin{document}
\author{Draft}

\section{HST astrometry}
We adopt the VLA 5\,GHz map of BLAH resolution as the reference coordinate frame and align the optical image. We shifted the 
latter to the east by BLAH" in R.A and BLAH in declination., which is consistent with the typical astrometric precision of the HST image. 
The radio image is calibrated employing well-monitored phase calibrator, with positions known to $\sim$1 mas. 
We estimate the absolute alignment of the 5 GHz and CO(J=2-1) coordinate frames should
be better than 0.1", leaving aside uncertainties relating to the SNR and beam size.

%The astrometry of the HST images was firstly calibrated against a wider-field
%optical image of the cluster which had in turn been aligned onto the FK5
%coordinate system to an rms precision of ~0.2".

@@

% Integrated line flux: 37.509 Jy km/s over chan=[49,70] (FWZI) of sigma = 13.3mJy /B/channel of 35.87 km/s per channel
%  57.753459930419922        10.658399798838524
% 38.906448364257812        54.223567641493943
% 258.26144409179688        57.450322398332851
% 2.2153112888336182        2.9563491085933622

% If we fit gaussian without the continuum to minimize error:
% 58.848747253417969        10.030933764224825
% 36.368530273437500        54.749284630860281
% 276.93515014648438        54.753666156237443

We detect unresolved CO($J$ = 3 $\rightarrow$ 2) line emission toward the
background galaxies in RXJ1131-1231.
We extract the spectrum and fit a single-component Gaussian as shown in Figure
\ref{fig:co32spec}
yielding peak flux density of 57.8 $\pm$ 10.7 mJy, the FWHM of the Gaussian fit
is 608 $\pm$ 57 km s$^{-1}$. The integrated line flux is 37.509$\pm$ 2.24 Jy km/s, this does not include the uncertainties in the calibration.

\begin{figure}[tbph]
\centering
\includegraphics[width=0.5\textwidth]{../Figures/co32_spec_bin2.eps}	  
\caption{
CO32 line spectrum
 \label{fig:co32spec}}
\end{figure}

% line free channels:1,118,160,600
% nchan =(117+600-160+1) = 558
% sigma =  0.83 mJy/B

At spatial position of CO emission, No significant continuum emission was
detected from the line-free channels down to a 3$\sigma$ limit of 2.49mJy Beam\pmOne.
(also as suggested in the fitted Gaussian to the spectrum continuum level: 2.2 $\pm$ 3.0 mJy).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{CO($J$ = 2 $\rightarrow$ 1) line emission}

% intensity over chan 124, 156 of rms ~ 1.451 mJy/ Beam/ch
% velocity resolution per bin: 21.528154 km/s

%sigma_mom0 = 0.43  over chan: 127, 155

@@

We construct the velocity-integrated (0th moment) map of the CO($J$ = 2
$\rightarrow$ 1) emission using the uv-continuum subtracted data, the
velocity-integrated 
CO($J$ = 2 $\rightarrow$ 1) line flux is 20.3 $\pm$ 0.2 Jy km s$^{-1}$.

We place an upper limit on HNC (J=2-1) line emission at the rest-shifted frequency 140 GHz in the foreground galaxy at $z\sim$0.295) of $\sigma$ = 1.451mJy per channel per beam. Assuming a typical line width of 300 \kms, this corresponds to a 3$\sigma$ limit of 4.353 mJy \kms beam\pmOne.

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.35\textwidth]{../Figures/{F555WCO21_mom0_single.invertedgray}.eps}	   
\includegraphics[width=0.35\textwidth]{../Figures/F555W_REDCentBLUE.png}
\includegraphics[width=0.55\textwidth]{../Figures/SpecCO21_twinx.eps}
\caption{
0th Moment map of CO(2-1) emission on HST F555W. moment-0: no clipping, of $\sigma$ 0.43 mJy beam\pmOne. 
Spectrum. Velocity scale w.r.t z=0.655
 \label{fig:CO21mom0}}
\end{figure*}

\begin{figure}[tbph]
\centering
\includegraphics[width=0.5\textwidth]{../Figures/CO_highOmom_CLIP5sigma}       
\caption{
1st and 2nd order moments, clipped at 5 $\sigma$. 1st moment contour steps of 50 \kms, 2nd moment steps of 100 \kms.
velocity range in z=0 frame = [-530.33, 72.73] \kms
chan = [127, 155] 
sigma = 0.16821825 Jy \kms per Beam
theshold: 5*sigma = 7.2550e-3 Jy per beam (per channel)
 \label{fig:highOmoments}}
\end{figure}

\begin{figure*}[tbph]
\centering
\includegraphics[width=\textwidth]{../Figures/co_channel_maps.eps}	 %
\caption{
Black crosses indicate the position of the lensed AGN (components ABCD) and the central white-filled star indicates the
position of the foreground lensing galaxy (component G) as detected in the HST image.
 \label{fig:chanmap}}
\end{figure*}

\begin{figure*}[tbph]
\centering
\includegraphics[width=\textwidth]{../Figures/spatialSpec_offsetShifted.eps}   
\caption{ 
Spatial spectra, binned by 3 pixels in each direction (1\farcs5)
 \label{fig:spatialSpec}}
\end{figure*}

@@

% 2mm continuum averaged over chan 1 120 165 360
% number of channels = 316
% sigma = 1.451 mJy/B / sqrt(316) = 0.081625 mJy/B 
% go noise on map (whole map) after cleaning: 89.274 µJy/B
% F = 1.2 mJy (integrated spatially, from ~ 1 sigma contour; 150 pixels)

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{SED}

We fit SED models to the photometry of dust emission in RXJ1131-1231 with a power-law attached to the blue side and including the 24.0\micron data from Spitzer/MIPS to constrain the dust peak.

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.8\textwidth]{../Figures/FullSED.eps}	 
\caption{VLA 5GHz continuum and PdBI 2mm continuum
TODO: change sym indicating the VLA data, (now two points at the same frequency), change sym for the 2 points on 2mm PdBI (now integrated and peak), might want to extract flux after removing a point source model.
Note THAT the WISE flux is higher than the IRAC data, probably just due to the smaller aperture used in Spitzer flux extraction, which might not be resolving the source and not including everything. 
Might want to add NVSS constraints.
 \label{fig:}}
\end{figure*}
